{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-11 Paper/main.tex
Meeting Changes

	This paper introduces Functional Linear Regression in a scalar-on-function setting. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional. 
	We introduce two ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, functional principal component regression. Both methods depend on a parameter called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\

@@

	Each element of a Hilbert space can be expressed in terms of a corresponding basis. Using a Fourier expansion of an element $x \in \mathbb{H}$ w.r.t. a basis $S = \{s_n\}$ leads to the following representation.
	\begin{equation}
		x = \sum_{j = 1}^{\infty}{\langle x, s_j \rangle}s_j
	\end{equation}

@@

	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}\label{L_2}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$, but analogous constructions can be made for different domains. Denoted by $\mathbb{L}^2[0,1]$, this space consists of all $\mu$-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition in which $\mu$ denotes the Lebesgue-measure.
	\begin{equation}
		\lvert \lvert f \rvert \rvert_2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

@@

	One very important question in this context is how the coefficients $a_j$ for $j \in \mathcal{I}$ are derived for a given function $x(t)$. For the purposes of this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing these bases are found in Section \ref{Basis_Plots} of the Appendix.
	\vspace{-0.2cm}

	\paragraph{Monomial Basis}\label{Monomial_basis}
	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use the monomials as a basis. For entire functions $f(t)$, such as polynomials, the exponential function, or trigonometric functions, we can express the function as a potentially infinite but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

@@

	A typical setup is described by \cite{Goldsmith_2011} in which an explicit smoothness term is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting the $L$ sufficiently high. To provide intuition for this approach, let 
	\begin{equation}
		PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
	\end{equation}

	denote the penalized residual sum of squares as notated by \cite{ramsay_functional_2005} for the derivative of order $m$. A typical choice is the second derivative, as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty. The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be archived by different criteria as shown in \cite{ThomasLee_2003}.

@@

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a random function $X: \Omega \mapsto \mathbb{L}^2[0,1]$, it is possible to represent its realizations in terms of the stochastic process. To do so, we define the mean and covariance functions of $X(\omega)$.
	\begin{equation}\label{MeanFunction}
		\mu(t) = \mathbb{E}\left[ X(\omega)(t) \right]
	\end{equation}
	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}

@@

	\subsubsection{Estimation using Basis-Representation}\label{basis_exp_transf}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Let $\{\phi_j(t) \: \vert \: j \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
	\begin{equation}
		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
	\end{equation}
	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.	
	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression.

	Define therefore the following objects
	\begin{equation}\label{regressor_mat_1}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{Z}_{N,1} & \dots & \tilde{Z}_{N,J}
		\end{pmatrix}
	\end{equation}

@@

	The performance of this estimation procedure depends in part on the quality of the approximation in Equation \ref{simplified_model_basis_equation}. Due to the nature of basis representations, the approximation error can only decrease with an increasing number of basis functions. Contrary to this effect, we have the potential benefits of introducing some amount of smoothing into the procedure. Because of this tradeoff, it is intuitively unclear, what the effects of different choices for the number of basis functions might be.

@@

	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in terms of the Eigenfunctions of $X(\omega)(t)$.
	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
		\end{split}
	\end{equation}

	\newpage
	As these theoretical Eigenfunctions and Eigenvalues are unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.
	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
		\end{split}
	\end{equation}

@@

	As in the previous case, the performance of this estimation depends in parts on the quality of the approximation made during the derivation of this estimator. Here, the interactions are even more complicated. Even though the approximations exhibit smaller errors when a larger number of basis functions is used, the interplay of smoothing in the construction of the functional principal components and the choice of a number of FPC's to be used in the linear regression makes the behavior of this estimator difficult to predict.

@@

	Instead of generating data from scratch, we use the gasoline data set from R package \textit{refund}, which consists of 60 samples of Near-infrared (NIR) absorption curves measured in increments of 2 nm from 900 to 1,700 nm, and a response variable, the octane number. We chose this setup to improve the approach towards the application in which we predict the octane numbers from the gasoline data set.	
	We introduced different bases in Section \ref{bases} and demonstrated the importance of the truncation parameter $L$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we rely on the estimation strategies with the introduced bases and focus on choosing the truncation parameter $L$ as well as the number of FPC's by ten-fold CV using the Mean-Squared Prediction Error (MSPE).

@@

    \subsection{Simulation setup}
	The simulation study follows \cite{Reiss_2007b} as a guideline. Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, that differ in their smoothness, are created to compare our methods with differing true coefficient functions.
	\begin{equation}
    	f_1(t) = 401 \left[ 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) \right]
    \end{equation}
    \begin{equation}
    	\begin{split}
    		f_2(t) = 401  \Bigg[ & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)} \Bigg]
    	\end{split}
    \end{equation}

@@

	\subsubsection{Basis Expansion Regression}
	The following results originate from the \hyperref[basis_exp_transf]{Estimation using Basis-Representation}, in which we transform the smooth curves to perform scalar-on-function regression. Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions for all bases.

	\paragraph{Monomial Basis}
	Due to the increasing collinearity problems for higher numbers of Monomial basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability. For reasons outlined in \ref{Monomial_basis}, they seem suited for $f_1$, where it shows a better performance than B-splines. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In the case of $f_2$, this basis shows the weakest performance out of all bases, for which Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide visual evidence. It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behavior at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) Monomial basis functions for the high(low) signal-to-noise ratio. 
	\vspace{-0.2cm}

@@

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high (low) signal-to-noise ratio. As for the B-splines basis, the simulation chooses a smaller number of basis functions for the noisy responses and a higher number for the high signal-to-noise responses. The Fourier basis performs the best for each setup for the basis expansion regression. Several reasons could contribute to this. First, especially $f_1$ shows similar curvature across the domain while the curvature of $f_2$ does at least not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval, lending itself to a periodic representation.
	\vspace{-0.2cm}

	\subsubsection{Functional Principal Component Regression}
	The model used for the FPCR is described in \hyperref[fpc_exp_transf]{Estimation using Functional Principal Components}. The selection of the truncation parameter $L$ is difficult since the approximated Eigenfunctions from the decomposition are influenced by the choice of $L$. In addition, the choice of the number of FPC's adds to the complexity of the model. Some eigenfunctions, which might contain important information, could correspond to small Eigenvalues and, therefore, be omitted as described in Section \ref{sim_motivation}. But since the FPCR is ultimately estimated with a linear model containing the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by $n_{FPC} \in \{2, 3, 4 \}$. It seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's. This might be because this dependency is too complex to draw conclusions with this simulation study. Therefore, we will limit ourselves to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account. This is indicated by the fact that the same number of basis functions is chosen for the different signal-to-noise ratios. A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the responses.

	\paragraph{Monomial Basis}
	For $f_1,Y_1$, the cross-validated MSPE seems to decrease in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} = 2, 3, 4$). For the noisy responses of $f_1,Y_2$ we find sign of overfitting for $n_{FPC}$ = 4. In  $f_2$, we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions. The Monomial basis shows the weakest performance for all three bases in each setting.
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	For $f_1,Y_1$, the MSPE suggests that models with a higher number of FPC's perform better. While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$. In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting for $n_{FPC} = 4$. Similar to the two setups with $f_1$, the chosen number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} = 2, 3, 4$)
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	In $f_1,Y_1$, the MSPE decreases in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting when using $n_{FPC} = 4$. Both specifications using $f_1$ select the lowest number of basis  possible. $f_2,Y_1$ displays the greatest relative decline of MSPE in the increasing number of FPC's, but in absolute values, therefore acknowledging the higher noise responses for $f_2,Y2$, the decline of MSPE is similar to the decline observed for $f_2,Y_2$. Both configurations of $f_2$ use 5, 15 and 7 basis functions for $n_{FPC} = 2, 3, 4$. The basis shows the lowest MSPE for all four settings.
	\vspace{-0.2cm}

	\subsubsection{Interpretation and Relevance for Application}
	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$, only little bias seems to be introduced when choosing a small number of basis functions. For $f_2$, a higher number of basis functions seems appropriate. This could result from the inherent peculiarities of $f_2$ that are more pronounced with higher $L$, therefore choosing higher numbers of basis functions since the bias is decreasing faster than the variance is increasing in the number of basis functions compared to $f_1$. The described convex behavior of the MSPE might also be partially attributable to the bias-variance tradeoff.

>>>>

	This paper introduces Functional Linear Regression in a scalar-on-function setting. The distinct feature of this framework is that the regressor is a function, which makes a different approach to estimation necessary because the problem of estimating an unknown coefficient function is inherently infinite-dimensional. 
	We introduce two ways of translating this infinite-dimensional problem into a finite-dimensional problem that can be addressed using theory from multivariate regression: First, a so-called basis expansion of the coefficient function, and second, Functional Principal Component Regression (FPCR). Both methods depend on a parameter called a truncation parameter for a functional basis, and this paper focuses on exploring the selection of these parameters using cross-validation.\\

@@

	Each element of a Hilbert space can be expressed in terms of a corresponding basis. Using a Fourier expansion of an element $x \in \mathbb{H}$ with respect to a basis $S = \{s_n\}$ leads to the following representation.
	\begin{equation}
		x = \sum_{j = 1}^{\infty}{\langle x, s_j \rangle}s_j
	\end{equation}

@@

	\subsection{Random Functions in the Hilbert Space of Square-Integrable Functions}\label{L_2}
	In functional data analysis, one Hilbert space of particular importance is the space of square-integrable functions on $[0,1]$, but analogous constructions can be made for different domains. Denoted by $\mathbb{L}^2[0,1]$, this space consists of all Lebesgue-measurable functions $f(t)$ on $[0,1]$ that fulfill the following condition.
	\begin{equation}
		\lvert \lvert f \rvert \rvert_2 = \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

@@

	One important question in this context is how the coefficients $a_j$ for $j \in \mathcal{I}$ are derived for a given function $x(t)$. In this paper, this process will remain a black box, but detailed information on the derivation of these coefficients can be found in chapter 4 of \cite{ramsay_functional_2005}.
	Three examples of bases used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing these bases are found in Appendix \ref{Basis_Plots}.

	\newpage
	\paragraph{Monomial Basis}\label{Monomial_basis}
	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use the monomials as a basis. For entire functions $f(t)$, such as polynomials, the exponential function, or trigonometric functions, we can express the function as a potentially infinite but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

@@

	\newpage
	A usual setup is described by \cite{Goldsmith_2011} in which an explicit smoothing term is used to tune the smoothness of the estimator $\hat{\beta}(t)$ while setting setting the number of basis functions sufficiently high. To provide intuition for this approach, let 
	\begin{equation}
		PSSE_\lambda(\alpha, \beta) = \sum_{i = 1}^{N} \left[ Y_i -\alpha -\int_0^1 \beta(t)X_i(t)dt \right]^2 + \lambda \int \left[D^m\beta(t)\right]^2 dt
	\end{equation}

	denote the penalized residual sum of squares for the derivative of order $m$. A typical choice is the second derivative, as highly variable functions are expected to exhibit large second derivatives and therefore a larger penalty. The smoothing parameter $\lambda$ is set to minimize the $PSSE_\lambda(\alpha, \beta)$, which can be achieved by different criteria as shown in \cite{ThomasLee_2003}.

@@

	\newpage
	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a random function $X: \Omega \mapsto \mathbb{L}^2[0,1]$, it is possible to represent its realizations in terms of the stochastic process. To do so, we define the mean and covariance functions of $X(\omega)$.
	\begin{equation}\label{MeanFunction}
		\mu(t) = \mathbb{E}\left[ X(\omega)(t) \right]
	\end{equation}
	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}

@@

	\subsubsection{Estimation using Basis-Representation}\label{basis_exp_transf}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Let $\{\phi_j(t) \: \vert \: j \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
	\begin{equation}
		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
	\end{equation}
	This enables us to write Equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.	
	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	A model in the form of Equation \ref{simplified_model_basis_equation} naturally lends itself to be estimated using theory from multivariate linear regression. 
	Define therefore the following objects.
	\begin{equation}\label{regressor_mat_1}
		Y = \begin{pmatrix}
			y_1 \\ \vdots \\ y_n
		\end{pmatrix}, \quad
		Z = \begin{pmatrix}
			1 & \tilde{Z}_{1,1} & \dots & \tilde{Z}_{1,J} \\
			\vdots & \vdots & \ddots & \vdots \\
			1 & \tilde{Z}_{N,1} & \dots & \tilde{Z}_{N,J}
		\end{pmatrix}
	\end{equation}

@@

	The performance of this estimation procedure depends in part on the quality of the approximation in Equation \ref{simplified_model_basis_equation}. Due to the nature of basis representations, the overall approximation error $\delta(t)$ can only decrease with the number of basis functions. However, in specific points $t_0$ which might coincide with high predictive power for the response, the error $\delta(t_0)$ could increase, potentially increasing the prediction error.
	In addition, we have the potential benefits of  smoothing such as reducing the potential of overfitting functional noise and reducing the degrees of freedom in the estimation. Because of this tradeoff between a reduction in the overall approximation error and beneficial smoothing properties, increasing the number of basis function and thereby decreasing the approximation error is not necessarily beneficial for the prediction accuracy. 
	Therefore, the behavior of the estimator when changing the truncation parameter $L$ is not intuitively clear even if we stay in the same basis system.

@@

	Using the Karhunen-Lo\'{e}ve Expansion to represent $X(\omega)$, it is also possible to express the data generating process in terms of the Eigenfunctions of $X(\omega)$.
	\begin{equation}
		\begin{split}
			Y(\omega) &= \alpha + \int_{0}^{1} {\color{red}X(\omega)(s)} \beta(s) \mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1} {\color{red}\left(\mu(s) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon(\omega)\\
			&= {\color{teal}\alpha + \int_{0}^{1} \mu(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\int_{0}^{1} \nu^m(s) \beta(s) \mathrm{d}s} + \epsilon(\omega)
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\infty} \xi^m(\omega) {\color{violet}\beta^m} + \epsilon(\omega)
		\end{split}
	\end{equation}

	As these theoretical Eigenfunctions and Eigenvalues are unknown, the corresponding equation in sample analogs is more interesting as a representation of an observation.
	\begin{equation}
		\begin{split}
			y_i &= \alpha + \int_{0}^{1} {\color{red}x_i(s)} \beta(s) \mathrm{d}s + \epsilon_i
			= \alpha + \int_{0}^{1} {\color{red}\left(\hat{\mu}(s) + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i \hat{\nu}^m(s)\right)} \beta(s) \mathrm{d}s + \epsilon_i\\
			&= {\color{teal}\alpha + \int_{0}^{1} \hat{\mu}(s) \beta(s) \mathrm{d}s} + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i {\color{violet}\int_{0}^{1} \hat{\nu}^m(s) \beta(s) \mathrm{d}s} + \epsilon_i
			= {\color{teal}\bar{\alpha}} + \sum_{m = 1}^{\mathcal{O}} \hat{\xi}^m_i {\color{violet}\hat{\beta}^m} + \epsilon_i
		\end{split}
	\end{equation}

@@

	As in the previous case, the performance of this estimation depends in parts on the quality of the approximations in the derivation of this estimator. The interactions are even more complex. Even though the approximations exhibit smaller errors when a larger number of basis functions is used, the interplay of the chosen way of smoothing in the construction of the FPC's and the choice of a number of FPC's used in the linear regression makes the behavior of this estimator difficult to predict.

@@

	Instead of generating data from scratch, we use the gasoline data set from R package \textit{refund}, which consists of 60 samples of Near-infrared absorption curves measured in increments of 2 nm from 900 to 1,700 nm, and a response variable, the octane number. We chose this setup to improve the approach towards the application in which we predict the octane numbers from the gasoline data set.	
	We introduced different bases in Section \ref{bases} and demonstrated the importance of the truncation parameter $L$ for the estimation in Section \ref{Scalar_on_function_regression}. For the simulation study, we use Basis Expansion Regression and Functional Principal Component Regression (FPCR) with the introduced bases and focus on choosing the truncation parameter $L$ as well as the number of FPC's by ten-fold CV using the Mean-Squared Prediction Error (MSPE).

@@

    \subsection{Simulation setup}
	The simulation study follows \cite{Reiss_2007b} as a guideline. Two different true coefficient functions,  $f_1(t)$ and  $f_2(t)$, that differ in their smoothness, are created to compare our methods with differing true coefficient functions.

	\begin{equation}
    	f_1(t) = 401 \left[ 2\sin(0.5\pi t) + 4\sin(1.5 \pi t) + 5\sin(2.5 \pi t) \right]
    \end{equation}
    \begin{equation}
    	\begin{split}
    		f_2(t) = 401  \Bigg[ & 1.5 \exp{\left(\frac{-0.5(t-0.3)^2}{0.02^2}\right)} - 4 \exp{\left(\frac{-0.5(t-0.45)^2}{0.015^2}\right)} \\
    				 & + 8 \exp{\left(\frac{-0.5(t-0.6)^2}{0.02^2}\right)} -  \exp{\left(\frac{-0.5(t-0.8)^2}{0.03^2}\right)} \Bigg]
    	\end{split}
    \end{equation}

@@

	\subsubsection{Basis Expansion Regression}
	These results follow from the model introduced in Section \ref{basis_exp_transf}, in which we transform the smoothed curves to perform scalar-on-function regression. Examining the results, it appears that the cross-validated MSPE exhibits a convex behavior in the number of basis functions for all bases.

	\paragraph{Monomial Basis}
	Due to the increasing collinearity problems for higher numbers of Monomial basis functions, simulations were conducted up until the sixth monomial, which already shows signs of numerical instability. For reasons outlined in Section \ref{Monomial_basis}, they seem suited for $f_1$, where it shows a better performance than B-splines. A hypothesis for this could be that $f_1$ is an entire function, which can be well approximated with a power series. In the case of $f_2$, this basis shows the weakest performance out of all bases, for which Figures \ref{basis_expansion_2_1} and \ref{basis_expansion_2_2} provide visual evidence. It seems like $\hat{\beta}(t)$ is not changing in the amount of noise and shows exaggerated behavior at the boundaries. This weakness is especially pronounced in the MSPE for $f_2,Y_1$. For $f_1$, the simulation selects 5(3) and for $f_2$ 5(5) Monomial basis functions for the high (low) signal-to-noise ratio. 
	\vspace{-0.2cm}

@@

	\paragraph{Fourier Basis}
	For $f_1$, the simulation chooses a smaller number of Fourier basis functions, 5(3) and a higher number for $f_2$, 9(7) for the setup with the high (low) signal-to-noise ratio. As for the B-splines basis, the simulation chooses a smaller number of basis functions for the noisy responses and a higher number for the high signal-to-noise responses. The Fourier basis performs the best for each setup for the Basis Expansion Regression. Several reasons could contribute to this. First, especially $f_1$ shows similar curvature across the domain while the curvature of $f_2$ does at least not display any erratic jumps. Second, both functions feature periodic behavior. Third, $f_2$ does have the same value at the start- and the end of the interval, lending itself to a periodic representation.
	\vspace{-0.2cm}

	\subsubsection{Functional Principal Component Regression}
	The model used for the FPCR is described in Section \ref{fpc_exp_transf}. The selection of the truncation parameter $L$ is difficult since the approximated Eigenfunctions from the decomposition are influenced by the choice of $L$. In addition, the choice of the number of FPC's adds to the complexity of the model. Some eigenfunctions, which might contain important information, could correspond to small Eigenvalues and, therefore, be omitted as described in Section \ref{sim_motivation}. But since the FPCR is ultimately estimated with a linear model containing the corresponding scores as regressors, the relevant degrees of freedom in the estimation of the ultimate model are not affected by $L$, but only by $n_{FPC} \in \{2, 3, 4 \}$. It seems that neither a convex behavior of the MSPE nor any clear relationship can be observed between the number of basis functions and the number of FPC's. This might be because this dependency is too complex to draw conclusions with this simulation study. Therefore, we will limit ourselves to a brief description. In this simulation, the cross-validated choice of basis functions indicates that the FPCR might not take the differing signal-to-noise ratios of the responses into account. This is indicated by the fact that the same number of basis functions is chosen for the different signal-to-noise ratios. A possible explanation might be that the FPC's, which affect the relevant degrees of freedom, are solely calculated from the smoothed curves, not considering the responses.

	\paragraph{Monomial Basis}
	For $f_1,Y_1$, the cross-validated MSPE seems to decrease in the number of FPC's and chosen basis functions for both the high and the low signal-to-noise ratio ($4,5,6$ basis functions for $n_{FPC} = 2, 3, 4$). For the noisy responses of $f_1,Y_2$ we find signs of overfitting for $n_{FPC}$ = 4. In  $f_2$, we also observe a decreasing MSPE in the number of FPC's, but no clear relationship for the chosen basis functions. The Monomial basis shows the weakest performance out of all three bases in each setting.
	\vspace{-0.2cm}

	\paragraph{B-spline Basis}
	For $f_1,Y_1$, the MSPE suggests that models with a higher number of FPC's perform better. While the number of basis functions stays at five for $n_{FPC} = 2,3$, it increases to 6 basis functions for $n_{FPC} = 4$. In $f_1,Y_2$, the cross-validated MSPE is only slightly affected by $n_{FPC}$, but lowest for $n_{FPC} = 3$, indicating the possibility of overfitting for $n_{FPC} = 4$. Similar to the two setups with $f_1$, the chosen number of basis functions for $f_2$ is increasing in the number of FPC's (4, 6, 23 for $n_{FPC} = 2, 3, 4$).
	\vspace{-0.2cm}

	\paragraph{Fourier Basis}
	In $f_1,Y_1$, the MSPE decreases in $n_{FPC}$ while the results in $f_1,Y_2$ might indicate overfitting for $n_{FPC} = 4$. Both specifications using $f_1$ select the lowest number of basis functions possible. This is interesting as the number of FPC's puts a binding lower bound on the number of basis functions used in their construction. An exploration of the implications of this fact is out of the scope of this paper. Both configurations of $f_2$ use 5, 15 and 7 basis functions for $n_{FPC} = 2, 3, 4$. The basis shows the lowest MSPE for all four settings.
	\vspace{-0.2cm}

	\subsection{Interpretation and Relevance for Application}
	A possible explanation applicable to the setups performing Basis Expansion Regression might be the effect of the Bias-Variance tradeoff and the following hypothesis: For $f_1$, only little bias seems to be introduced when choosing a small number of basis functions. For $f_2$, a higher number of basis functions seems appropriate. This could result from the inherent peculiarities of $f_2$ that are more pronounced with higher $L$, therefore choosing higher numbers of basis functions since the bias is decreasing faster than the variance is increasing in the number of basis functions compared to $f_1$. The described convex behavior of the MSPE might also be partially attributable to the bias-variance tradeoff.  
	This convex behavior was not observed for the FPCR where no clear relationship between the basis functions and the number of FPC's could be found. The MSPE of FPCR seems to be comparatively more stable when changing the number of basis functions than for Basis Expansion Regression. It seems like the chosen number of FPC's is more significant, especially for the two high signal-to-noise ratio settings which display a higher absolute and relative decrease of MSPE in $n_{FPC}$.\\

	To examine this relationship further, we conducted additional simulations (Appendix \ref{Tables_sim_additional}) for B-spline basis specifications with a large truncation parameter $L \in \{50, 70\}$ for $n_{FPC} \in \{2, \dots, 7 \}$. We can find potential signs of overfitting in all setups for $L = 70$. For $L = 50$, signs of overfitting can be observed for the setups with the noisy responses. The additional simulations revealed evidence for a relationship from $n_{FPC} = 3$ onwards for all setups. For $n_{FPC} \in \{3, \dots, 7 \}$, the ten-fold cross-validated MSPE is always lower for 50 than for 70 basis functions. This might be the first sign of an $L$ that is chosen too large and creates undersmoothing. It seems that once a sufficient number of basis functions is used to expand the curves, FPCR with B-splines performs better using a lower number of basis functions. While a higher number of $n_{FPC}$ decreases the MSPE of $f_1,Y_1$ and $f_2,Y_1$ for $L = 50$ compared to the main simulations, this does not hold true for the two setups with noisy responses. This strengthens our hypothesis of the high importance of $n_{FPC}$ for the high signal-to-noise ratio setup. For $n_{FPC} \in \{2, 3, 4 \}$, the additional B-splines simulations perform worse for these high number of basis functions compared to the main simulation.  This might indicate beneficial attributes of a lower truncation parameter in settings with a lower number of $n_{FPC}$.
